### 2023-11-17 chapters/paper_review/04_benchmarking.tex
Fix notation for layer-number and timestep

\subsection{Experiment settings for evaluating SSL techniques}
A common way to benchmark SSL techniques and show their efficacy is to
fine-tune a pre"=trained SSL model for a supervised downstream task.
Depending on the corpora used in pre"=training and fine"=tuning, techniques can
be benchmarked in terms of their capability to transfer knowledge across datasets
(i.e., using pre"=training corpora that differ from the fine"=tuning ones), their
benefit when training with limited labeled examples (i.e., sampling a subset of
labeled examples for fine"=tuning), or their improvement over a fully supervised
baseline (i.e., using the entire training split of downstream datasets for
fine"=tuning). \cref{table:method_data_setting,table:method_data_setting_2} summarize experiment settings used in the
SSL literature, including the pre"=training corpora, downstream tasks and datasets,
and the amount of fine"=tuning labels used, which indicates the targeted
benchmarking scenario as discussed above. Note that there are a variety of ways
to fine-tune pre"=trained networks (e.g., fine-tune the entire network,
freeze certain layers during fine"=tuning, and add various architectures of
prediction layers to pre"=trained networks). We here omit
descriptions of these choices; readers can consult the
original publications for details.

>>>>

\subsection{Experiment settings for evaluating SSL techniques}
A common way to benchmark SSL techniques and show their efficacy is to
fine-tune a pre"=trained SSL model for a supervised downstream task.
Depending on the corpora used in pre"=training and fine"=tuning, techniques can
be benchmarked in terms of their capability to transfer knowledge across datasets
(i.e., using pre"=training corpora that differ from the fine"=tuning ones), their
benefit when training with limited labeled examples (i.e., sampling a subset of
labeled examples for fine"=tuning), or their improvement over a fully supervised
baseline (i.e., using the entire training split of downstream datasets for
fine"=tuning). \Cref{table:method_data_setting,table:method_data_setting_2} summarize experiment settings used in the
SSL literature, including the pre"=training corpora, downstream tasks and datasets,
and the amount of fine"=tuning labels used, which indicates the targeted
benchmarking scenario as discussed above. Note that there are a variety of ways
to fine-tune pre"=trained networks (e.g., fine-tune the entire network,
freeze certain layers during fine"=tuning, and add various architectures of
prediction layers to pre"=trained networks). We here omit
descriptions of these choices; readers can consult the
original publications for details.
